\documentclass[10pt,a4paper]{report}
\usepackage{bsymb,b2latex}
\begin{document}
\SingleHeader{BasicLibrary}
\MACHINE{BasicLibrary}{}{LibraryContext}{\\Basic function of the library}
\VARIABLES{
	\Variable{registered\_users}{The users registered in library system.}
	\Variable{books\_in\_library}{The books (title) in the library.}
	\Variable{copies\_in\_library}{Copies that the library has.}
	\Variable{copies\_on\_shelf}{Copies that are in the library(On bookshelf).}
	\Variable{copies\_on\_loan}{Copies that is already on loan.(Borrow pairs)}
	\Variable{library\_book\_sets}{The pairs of the book (title) and the copies in library.}
}
\INVARIANTS{
	\Invariant{inv1}{false}{$registered\_users \subseteq{} USER$}{\\The registered users need to be the users in the world.}
	\Invariant{inv2}{false}{$books\_in\_library \subseteq{} BOOK$}{\\The books that the library has need to be the books in the world.}
	\Invariant{inv3}{false}{$copies\_in\_library \subseteq{} COPY$}{\\The copies of the library has to be the copies in the world.}
	\Invariant{inv4}{false}{$copies\_on\_loan \in{} copies\_in\_library \pfun{} registered\_users$}{\\The copies on loan are pairs in particial function because the user can borrow no copy and copy can have no user to borrow.  }
	\Invariant{inv5}{false}{$copies\_on\_shelf = copies\_in\_library \setminus{} dom(copies\_on\_loan)$}{\\Copies on shelf is the all copies of the library minus the copies that have been borrowed.}
	\Invariant{inv7}{false}{$library\_book\_sets \in{} copies\_in\_library \tfun{} books\_in\_library$}{\\library book sets are pairs of total function of copies in library and books in library, because all books in library have copies and all copies in library must have a related book. }
	\Invariant{inv8}{false}{$library\_book\_sets \subseteq{} book\_sets$}{\\The book and copy relation in library is a subset of the book and copy relation in whole world.}
}
\EVENTS{
\INITIALISATION{false}{\\initialisation event}{
	\ACTIONS{false}{
		\Action{act1}{$registered\_users,books\_in\_library,copies\_in\_library,copies\_on\_shelf,copies\_on\_loan,library\_book\_sets \bcmeq{} \emptyset{},\emptyset{},\emptyset{},\emptyset{},\emptyset{},\emptyset{}$}{true}{}
	}
}
\EVT{AddBook}{false}{ordinary}{}{\\Add book event}{
	\ANY{
		\Param{book}{true}{The book which is going to be added.}
		\Param{copies}{true}{The related copies.}
		\Param{book\_set}{true}{The pairs between book and the copies.(To explain book and corresponding copies.)}
	}
	\GUARDS{true}{
		\Guard{grd1}{false}{$book \in{} BOOK$}{true}{\\The book needs to be one of the BOOK in the world.}
		\Guard{grd2}{false}{$book \notin{} books\_in\_library$}{true}{\\This book is not in the library.}
		\Guard{grd3}{false}{$copies \subseteq{} COPY$}{true}{\\Copies are copies in the world.}
		\Guard{grd4}{false}{$book\_set \subseteq{} book\_sets$}{true}{\\The pairs of book and copies are subset of all books and copies pairs in the world.(Copies are under the book title. However, not all copies under the book title are added to library.)}
		\Guard{grd5}{false}{$book\_set \in{} copies \tfun{} \{book\} $}{true}{\\Book set is the pairs of copies and book.}
	}
	\ACTIONS{true}{
		\Action{act1}{$books\_in\_library \bcmeq{} books\_in\_library \bunion{} \{book\}$}{true}{\\Add this book to library.}
		\Action{act2}{$copies\_in\_library \bcmeq{} copies\_in\_library \bunion{} copies$}{true}{\\Add all related copies to library.}
		\Action{act3}{$copies\_on\_shelf \bcmeq{} copies\_on\_shelf \bunion{} copies$}{true}{\\Put all copies on shelf.}
		\Action{act4}{$library\_book\_sets \bcmeq{} library\_book\_sets \bunion{} book\_set $}{true}{\\Add pairs to library ralation.}
	}
}
\EVT{UserRegister}{false}{ordinary}{}{\\User Register}{
	\ANY{
		\Param{new\_user}{true}{Use who want to be a member of the library.}
	}
	\GUARDS{true}{
		\Guard{grd1}{false}{$new\_user \in{} USER$}{true}{\\New user needs to be one of the USER.}
		\Guard{grd2}{false}{$new\_user \notin{} registered\_users$}{true}{\\New user cannot be a registered$\_$users.}
		\Guard{grd3}{false}{$registered\_users \neq{} USER$}{true}{\\Registered users cannot be more than users in the world.}
	}
	\ACTIONS{true}{
		\Action{act1}{$registered\_users \bcmeq{} registered\_users \bunion{} \{new\_user\}$}{true}{\\Add user to registered$\_$users.}
	}
}
\EVT{UserDeregister}{false}{ordinary}{}{\\User Deregister}{
	\ANY{
		\Param{user}{true}{Use who wants to deregister.}
	}
	\GUARDS{true}{
		\Guard{grd1}{false}{$user \in{} registered\_users $}{true}{\\The user who wants to deregister needs to be a registered user first. }
		\Guard{grd2}{false}{$copies\_on\_loan \pfun{} \{user\} = \emptyset{} $}{true}{\\The user does not have any book that are not returned.}
	}
	\ACTIONS{true}{
		\Action{act1}{$registered\_users \bcmeq{} registered\_users \setminus{} \{user\}$}{true}{\\Exclude the use from registered users. }
	}
}
\EVT{Borrow}{false}{ordinary}{}{\\Borrow copy event.}{
	\ANY{
		\Param{user}{true}{User wants to borrow copy.}
		\Param{copy}{true}{The copy of the user wants to borrow.}
	}
	\GUARDS{true}{
		\Guard{grd1}{false}{$user \in{} registered\_users$}{true}{\\The user needs to be a registered user.}
		\Guard{grd2}{false}{$copy \in{} copies\_on\_shelf$}{true}{\\Copy is not borrowed by other users.}
		\Guard{grd3}{false}{$card(copies\_on\_loan \ranres{} \{user\}) \in{} 0\upto{}4$}{true}{\\The user cannot hold more than 4 books.}
	}
	\ACTIONS{true}{
		\Action{act1}{$copies\_on\_shelf \bcmeq{} copies\_on\_shelf \setminus{} \{copy\}$}{true}{\\Remove copy from shelf.}
		\Action{act2}{$copies\_on\_loan \bcmeq{} copies\_on\_loan \bunion{} \{copy \mapsto{} user\}$}{true}{\\Give user the copy and add relation.}
	}
}
\EVT{Return}{false}{ordinary}{}{\\Return copy.}{
	\ANY{
		\Param{copy}{true}{The copy will be returned.}
	}
	\GUARDS{true}{
		\Guard{grd1}{false}{$copy \in{} dom(copies\_on\_loan)$}{true}{\\Copy needs to be a copy has a relation of borrow.}
	}
	\ACTIONS{true}{
		\Action{act1}{$copies\_on\_shelf \bcmeq{} copies\_on\_shelf \bunion{} \{copy\}$}{true}{\\Add this copy to shelf.}
		\Action{act2}{$copies\_on\_loan \bcmeq{} \{copy\} \domsub{} copies\_on\_loan$}{true}{\\Exclude the borrow relation from the library borrow relations.}
	}
}
}
\END
\end{document}
